### 2009-04-23 doc/storage_system/arc-storage-manual.tex
implementing the requested changes in the internal review comments

\tableofcontents                          %Comment if use article style
% \begin{verbatim}
%     Administrator's and user's manual
%     ---------------------------------
% 
%     Administrator's manual
%     - Quick start guide
%         - Checking the code out from the subversion
%         - Compiling and installing
%         - Modifying the configuration template
%         - Running the daemon
%         - Using the CLI tool
%     - Installation:
%         - Getting the source code from subversion
%         - Compilation details
%         - Installation
%     - Configuration:
%         - HED service config
%         - Centralized A-Hash
%         - Distributed A-Hash
%         - Librarian
%         - Shepherd
%         - Hopi
%         - Bartender
%         - Configuring inter-service trust: local listing of DNs, or using an A-Hash to store them
%         - Virtual organizations: how to configure HED to trust a VO
%     - Deployment scenarios:
%         - Single node: putting every service on one single node (including a storage node with Hopi)
%         - Centralized management: using seperate multiple storage nodes with Hopi, but leaving a central A-Hash, a Librarian and a Bartender on the central node
%         - Simple distribution: split the central node to three nodes, each of them has an A-Hash, a Librarian and a Bartender, and we have separate storage nodes
%         - One service per node: we have seperate nodes for all the services, any number of A-Hash nodes, any number of Librarian nodes, Bartender nodes, storage nodes
% 
%     User's manual
%     - Overview: what do you need to access a running ARC storage system
%     - Prototype command line tool
%         - Configuring the command line tool
%         - Creating the root collection
%         - Uploading files
%         - Creating collections
%         - Moving files
%         - Creating hardlinks
%         - Removing files
%         - Removing collections
%         - Close collections
%         - Modify access policies
%         - Working with mount points
%     - Grid jobs
%         - Configuring the ARC storage DMC
%         - Specifying files in job descriptions
%     - Accessing the system with FUSE
%         - Configuring the FUSE module
%         - Mounting the storage system
%         - Supported operations
%         - Limitations
%     
% \end{verbatim}

@@

Let's check the README file for all the dependencies, and install them:

@@

The storage system runs withen the \verb!arched! hosting environment daemon, which needs a configuration file which describes which services we want to run, and on which ports do we want to listen, etc.
Let's copy the template configuration files to the \verb!/etc/arc! directory:

@@

Let's add a new storage element to the system. We need to deploy a Shepherd service and a storage element service, which this time will be a `byteio' service. The `byteio' service implements a small part of the ByteIO interface, which means that it just put the entire file data into the SOAP message, so it is only suitable for small files.

@@

Let's install Berkeley DB as root (but you can use the \verb!--prefix! option of \verb!configure! to install it somewhere else than the default location).

@@

Let's configure the our first server (\verb!storage!). Here is the AHash part of the config:

@@

In this config we specify the second server as a peer. Let's configure the second server as well:

@@

In this config we specify the first server as a peer. So the two together will be able to form a replicated network with two nodes. But let's configure the thirs one:

@@

It is important that we need to make a fresh start, and remove the existing database, which was created by a different store:
\begin{verbatim}
$ sudo rm -r /var/spool/arc/*
\end{verbatim}

@@

If we have permissions to access some third-party storage solutions (e.g. dCache), we can create a mount point within the namespace of the ARC storage system which points to a third-party URL, and then we can use the client interface of the ARC storage to access the third-party storage as well. This is achieved by a module of the Bartender, called the `Gateway'. Currently only GridFTP access is supported, and for that we need to install the Globus libraries to our machines. Then we need to recompile our source for GridFTP support. The output of the \verb!configure! script should look like this:

@@

\item Create some entries in your collection:
\begin{verbatim}
   $ cd mnt/home/me
   $ emacs -nw fish
   catfish
   $ cat fish
   catfish
   $ cp fish fisk2
   $ ls -la
   drwxr-xr-x 5 me users  0 1970-01-01 01:00 .
   drwxr-xr-x 3 me users  0 1970-01-01 01:00 ..
   -rw-r--r-- 1 me users  8 1970-01-01 01:00 fish
   -rw-r--r-- 1 me users 28 1970-01-01 01:00 fish~
   -rw-r--r-- 1 me users  8 1970-01-01 01:00 fish2
\end{verbatim}

>>>>

\tableofcontents                          %Comment if use article style

@@

Let's check the README file for all the dependencies, and install them! We use `aptitude' here, but of course on other linux distribution you may use a different package management software, and the name of the packages may differ as well.

@@

The storage system runs within the \verb!arched! hosting environment daemon, which needs a configuration file which describes which services we want to run, and on which ports do we want to listen, etc.
Let's copy the template configuration files to the \verb!/etc/arc! directory:

@@

Let's add a new storage element to the system. A new storage element should be on a different physical machine, preferably in a different building to minimize the possibility of both storage elements being offline at the same time. But for testing purposes it is of course possible to run it on the same machine using different ports. We need to deploy a Shepherd service and a storage element service, which this time will be a `byteio' service. The `byteio' service implements a small part of the ByteIO interface, which means that it just put the entire file data into the SOAP message, so it is only suitable for small files.

@@

Let's install Berkeley DB as root (but you can use the \verb!--prefix! option of \verb!configure! to install it somewhere else than the default location). This should be done on all the machines:

@@

Let's configure our first server (\verb!storage!). Here is the AHash part of the config:

@@

In this config we specify the second server as a peer. Let's configure the second server (\verb!storage2!) as well:

@@

In this config we specify the first server as a peer. So the two together will be able to form a replicated network with two nodes. But let's configure the third one (\verb!storage3!):

@@

It is important that we need to make a fresh start on all the servers, and remove the existing database, which was created by a different store:
\begin{verbatim}
$ sudo rm -r /var/spool/arc/*
\end{verbatim}

@@

If we have permissions to access some third-party storage solutions (e.g. dCache via the GridFTP protocol), we can create a mount point within the namespace of the ARC storage system which points to a third-party URL, and then we can use the client interface of the ARC storage to access the third-party storage as well. This is achieved by a module of the Bartender, called the `Gateway'. Currently only GridFTP access is supported, and for that we need to install the Globus libraries to our machines. Then we need to recompile our source for GridFTP support. The output of the \verb!configure! script should look like this:

@@

\item Create some entries in your collection:
\begin{verbatim}
   $ cd mnt/home/me
   $ emacs -nw fish
   catfish
   $ cat fish
   catfish
   $ cp fish fish2
   $ ls -la
   drwxr-xr-x 5 me users  0 1970-01-01 01:00 .
   drwxr-xr-x 3 me users  0 1970-01-01 01:00 ..
   -rw-r--r-- 1 me users  8 1970-01-01 01:00 fish
   -rw-r--r-- 1 me users 28 1970-01-01 01:00 fish~
   -rw-r--r-- 1 me users  8 1970-01-01 01:00 fish2
\end{verbatim}
